---
title: "Lab 5"
author: "Katherine Rosencrance"
date: "10/26/2021"
output: 
  html_document: 
    toc: yes
    theme: cerulean
    number_sections: yes
    code_folding: hide
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```
# COnfidence Intervals

In this section we'll learn to use the `t-test()` function as a way to return the conifidence interval using the t-distribution

## Example 1

Create a mock sample of observation values and find the confidence interval, then report that

```{r}
pika_mass <- c(82, 94, 110, 70, 86, 99, 102)

pika_mean <- mean(pika_mass)

pika_sd <- sd(pika_mass)

pika_ci <- t.test(pika_mass)

pika_ci
```
### Risky and Tedious Way:
Mean pika mass at Paiute Pass is 91.9 g $\pm$ 13.5 g
(mean $\pm$ 1 standard deviation, n = 7) with a 95% confidence interval of {79.4, 104.4} g.

### High intitial investement but safer and better way

In-line code referencing to stored objects!

Use a single backtick on either side of a lowercase r to create an in-line bit of code

Mean pika mass at Paiute Pass is `r round(pika_mean, 1)` g $\pm$ `r round(pika_sd, 1)` g (mean $\pm$ 1 standard deviation, n = `r length(pika_mass)`) with a 95% confidence interval of [`r pika_ci$conf.int[1]`],[`r pika_ci$conf.int[2]`] g.
 
 
 # Two- sample t-test
 
 Use a two sample t test to test the null hypothesis that samples were drawn from populations with the same mean (difference in means = 0).
 
  - H0; means difference =0
  - HA; means difference is not =0
  
  This is a two sided t test bc no directionality is implied
  
  ## Example 1
  
```{r}
oak_trees <- c(29, 19, 22,30, 36, 45, 20, 7)

pine_trees <- c(48, 49, 50, 55, 44, 45, 43)
```
  
Is there a significant difference in mean heights for oak and pine trees?

```{r}
trees_t <- t.test(oak_trees, pine_trees)
```

The p-value of `r trees_t$p.value` means that there is a `r (trees_t$p.value) *100` % chance of taking random samples where their means are at least as different as the sample mean I have if they were drawn from populations with the same mean height.

